Some useful information of OCV for missing data

### 2018-02-11 analysis/OCVmissdataSetting.Rmd
Files commited by wflow_commit.

---
title: "Some useful information of OCV for missing data"
author: "wei wang"
date: 2018-01-25
output: html_document
---

@@

>>>>

---
title: "Some useful information of OCV for missing data"
author: "wei wang"
output: html_document
---

@@

## software

### SFAmix

http://beehive.cs.princeton.edu/software/

### sfa

http://stephenslab.uchicago.edu/software.html#sfa

### NBSFA

https://github.com/davidaknowles/nsfa

### R packages

```{r}
library(ssvd)
library(PMA)
library(softImpute)
```
